Stochastic Variance-Reduced Policy Gradient

### 2018-06-27 poster/poster.tex
Updated SVRPG box

@@

% % Draw a video
% \newlength{\FSZ}
% \newcommand{\drawvideo}[3]{% [0 0.25 0.5 0.75 1 1.25 1.5]
%    \noindent\pgfmathsetlength{\FSZ}{\linewidth/#2}
%    \begin{tikzpicture}[outer sep=0pt,inner sep=0pt,x=\FSZ,y=\FSZ]
%    \draw[color=lightblue!50!black] (0,0) node[outer sep=0pt,inner sep=0pt,text width=\linewidth,minimum height=0] (video) {\noindent#3};
%    \path [fill=lightblue!50!black,line width=0pt] 
%      (video.north west) rectangle ([yshift=\FSZ] video.north east) 
%     \foreach \x in {1,2,...,#2} {
%       {[rounded corners=0.6] ($(video.north west)+(-0.7,0.8)+(\x,0)$) rectangle +(0.4,-0.6)}
%     }
% ;
%    \path [fill=lightblue!50!black,line width=0pt] 
%      ([yshift=-1\FSZ] video.south west) rectangle (video.south east) 
%     \foreach \x in {1,2,...,#2} {
%       {[rounded corners=0.6] ($(video.south west)+(-0.7,-0.2)+(\x,0)$) rectangle +(0.4,-0.6)}
%     }
% ;
%    \foreach \x in {1,...,#1} {
%      \draw[color=lightblue!50!black] ([xshift=\x\linewidth/#1] video.north west) -- ([xshift=\x\linewidth/#1] video.south west);
%    }
%    \foreach \x in {0,#1} {
%      \draw[color=lightblue!50!black] ([xshift=\x\linewidth/#1,yshift=1\FSZ] video.north west) -- ([xshift=\x\linewidth/#1,yshift=-1\FSZ] video.south west);
%    }
%    \end{tikzpicture}
% }
% 
% \hyphenation{resolution occlusions}
% %%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  columns=4,
  grid=false,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=blue900,
  headerColorOne=blue800,
  headerColorTwo=blue800,
  headerFontColor=white,
  boxColorOne=white,
  boxColorTwo=lightblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.095\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  % {\includegraphics[height=9em]{./pics/airlab_logo_reflect.png}} 
  {\includegraphics[height=7.0em]{./pics/polilogo/logoPoliBlue_poster.png}}
%   {\hspace{3.5cm}}
  % Title
  {\bf\textsc{Stochastic Variance-Reduced Policy Gradient}\vspace{0.1em}}
  % Authors
  {\textsc{M. Papini, D. Binaghi, G. Canonaco, M. Pirotta and M. Restelli}\\ 
  {\normalsize \texttt{\{matteo.papini, marcello.restelli\}@polimi.it}},
  {\normalsize \texttt{\{damiano.binaghi, giuseppe.canonaco\}@mail.polimi.it}},  {\normalsize \texttt{\{matteo.pirotta\}@inria.fr}}
  }
  % University logo
  {% The makebox allows the title to flow into the logo, this is a hack because of the L shaped logo.
    %\includegraphics[height=9.0em]{./pics/PoliMI.pdf}%\hspace{.5cm}
    \includegraphics[height=4em]{./pics/inria_sc}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{SVRPG}{name=svrpg,column=1,span=2,
  	row=0,%1
  	%below=contrib
  }{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
We design an \textbf{SVRG}-like algorithm for the \textbf{PG} framework.

@@

\begin{minipage}[t]{.45\textwidth}
The easy part:
\begin{itemize}
	\item Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)
	\item \textbf{SVRG} idea: combine frequent \textbf{SG} with rare \textbf{FG} into a corrected gradient estimator $\gradBlack{\vtheta}$
	\item Two time scales: $1$ \textbf{epoch} $=m$ \textbf{iterations}
\end{itemize}
\end{minipage}
\hfill%
\begin{minipage}[t]{.45\textwidth}
Solving the RL challenges:
\begin{enumerate}
	\item Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)
	\item Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$
	\item Correct \chall{nonstationarity} with \textbf{importance weighting}	
\end{enumerate}
\end{minipage}

\begin{center}
	Introducing the \enhance{SVRPG} estimator:
\end{center}

\noindent\dotfill
\begin{tabu} to \textwidth{X[c]X[2c]X[c]}
	\multirow{2}{*}{
		\shortstack{
			\textbf{FG term}\\
			$\frac{1}{N}\sum_{i=1}^{N} g(\tau_i|\wt{\vtheta})$\\
			$\tau_i\sim\wt{\vtheta}$\\
			$N$ trajectories\\
			Accurate but \bad{expensive}\\
			$\downarrow$\\
			Updated once per \textbf{epoch}
		}
	}	 
	&\tikz[baseline]{ 
		\node[draw=myblue, very thick, inner sep=5pt]{\Large{$\wh{\nabla}_N J(\wt{\vtheta}) + \wh{\nabla}_B J({\vtheta}) - \omega(\vtheta, \wt{\vtheta}) \wh{\nabla}_B J({\wt{\vtheta}})$}
		};
	}  
	\vspace{0.5cm} 
	& \multirow{2}{*}{
		\shortstack{
			\textbf{Correction term}\\
			$\frac{1}{B}\sum_{i=1}^{B}\underbrace{\omega(\tau_i|\vtheta,\wt{\vtheta})}_{\textbf{imp. weight}}g(\tau_i|\wt{\vtheta})$\\
			Trajectories from SG term \\
			Ensures SVRG properties\\
			\bad{Distribution mismatch}\\
			$\downarrow$\\
			\textbf{importance weighting}\\
			$\downarrow$\\
			\bad{new source of variance}
		}
	} \\
	& \shortstack{
		\textbf{SG term}\\
		$\frac{1}{B}\sum_{i=1}^{B} g(\tau_i|\vtheta)$\\
		$\tau_i\sim\vtheta$\\
		$B<<N$ trajectories\\
		Computed at each iteration\\
		\\Cheap but \bad{high-variance}\\
		$\downarrow$\\
		Stabilized by other terms
	}
\end{tabu}

@@

\begin{minipage}[t]{.55\textwidth}
	Fundamental \textbf{SVRG} properties:
	\begin{enumerate}
		\item Unbiasedness: $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
		\item Vanishing variance: $\Var{\gradBlack{\vtheta}}\to0$ as $\vtheta\to\vtheta^*$
	\end{enumerate}
\vfill
\end{minipage}
\hfill%
\begin{minipage}[t]{.4\textwidth}
\textbf{Importance weighting}

>>>>

% box for algorithms
\newlength{\minipagewidth}
\newlength{\minipagewidthx}
\setlength{\minipagewidth}{0.99\textwidth}
\setlength{\minipagewidthx}{0.99\textwidth}
\setlength{\fboxsep}{1.5mm}
\addtolength{\minipagewidth}{-\fboxrule}
\addtolength{\minipagewidth}{-\fboxrule}
\addtolength{\minipagewidth}{-\fboxsep}
\addtolength{\minipagewidth}{-\fboxsep}
\addtolength{\minipagewidthx}{+\fboxsep}
\newcommand{\bookbox}[1]{
\par\medskip\noindent
\framebox[\columnwidth]{
\begin{minipage}{\minipagewidth} {#1} \end{minipage} } \par\medskip }

\newcommand{\bookboxx}[1]{\small
\par\medskip\noindent
\framebox[0.99\textwidth]{
\begin{minipage}{0.97\dimexpr\textwidth-\parindent\relax} {#1} \end{minipage} } \par\medskip }

@@

% % Draw a video
% \newlength{\FSZ}
% \newcommand{\drawvideo}[3]{% [0 0.25 0.5 0.75 1 1.25 1.5]
%    \noindent\pgfmathsetlength{\FSZ}{\linewidth/#2}
%    \begin{tikzpicture}[outer sep=0pt,inner sep=0pt,x=\FSZ,y=\FSZ]
%    \draw[color=lightblue!50!black] (0,0) node[outer sep=0pt,inner sep=0pt,text width=\linewidth,minimum height=0] (video) {\noindent#3};
%    \path [fill=lightblue!50!black,line width=0pt] 
%      (video.north west) rectangle ([yshift=\FSZ] video.north east) 
%     \foreach \x in {1,2,...,#2} {
%       {[rounded corners=0.6] ($(video.north west)+(-0.7,0.8)+(\x,0)$) rectangle +(0.4,-0.6)}
%     }
% ;
%    \path [fill=lightblue!50!black,line width=0pt] 
%      ([yshift=-1\FSZ] video.south west) rectangle (video.south east) 
%     \foreach \x in {1,2,...,#2} {
%       {[rounded corners=0.6] ($(video.south west)+(-0.7,-0.2)+(\x,0)$) rectangle +(0.4,-0.6)}
%     }
% ;
%    \foreach \x in {1,...,#1} {
%      \draw[color=lightblue!50!black] ([xshift=\x\linewidth/#1] video.north west) -- ([xshift=\x\linewidth/#1] video.south west);
%    }
%    \foreach \x in {0,#1} {
%      \draw[color=lightblue!50!black] ([xshift=\x\linewidth/#1,yshift=1\FSZ] video.north west) -- ([xshift=\x\linewidth/#1,yshift=-1\FSZ] video.south west);
%    }
%    \end{tikzpicture}
% }
% 
% \hyphenation{resolution occlusions}
% %%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  columns=4,
  grid=false,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=blue900,
  headerColorOne=blue800,
  headerColorTwo=blue800,
  headerFontColor=white,
  boxColorOne=white,
  boxColorTwo=lightblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.095\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  % {\includegraphics[height=9em]{./pics/airlab_logo_reflect.png}} 
  {\includegraphics[height=7.0em]{./pics/polilogo/logoPoliBlue_poster.png}}
%   {\hspace{3.5cm}}
  % Title
  {\bf\textsc{Stochastic Variance-Reduced Policy Gradient}\vspace{0.1em}}
  % Authors
  {\textsc{M. Papini, D. Binaghi, G. Canonaco, M. Pirotta and M. Restelli}\\ 
  {\normalsize \texttt{\{matteo.papini, marcello.restelli\}@polimi.it}},
  {\normalsize \texttt{\{damiano.binaghi, giuseppe.canonaco\}@mail.polimi.it}},  {\normalsize \texttt{matteo.pirotta@inria.fr}}
  }
  % University logo
  {% The makebox allows the title to flow into the logo, this is a hack because of the L shaped logo.
    %\includegraphics[height=9.0em]{./pics/PoliMI.pdf}%\hspace{.5cm}
    \includegraphics[height=4em]{./pics/inria_sc}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{SVRPG: stochastic variance-reduced policy gradient}{name=svrpg,column=1,span=2,
  	row=0,%1
  	%below=contrib
  }{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
We design an \textbf{SVRG}-like algorithm for the \textbf{PG} framework.

@@

\noindent\begin{minipage}[t]{.32\textwidth}
        \hlg{The easy part:}\\[.2cm]
%\begin{itemize}\compresslist
        $\bullet$~Take any \textbf{unbiased} policy gradient estimator $g(\tau|\vtheta)$ (\eg REINFORCE)\\[.15cm]
    $\bullet$~\textbf{SVRG} idea: combine \hly{frequent \textbf{SG}} with \hly{rare \textbf{FG}} into a corrected gradient estimator $\gradBlack{\vtheta}$\\[.15cm]
    $\bullet$~Two-time scales:\\ \hspace*{.8cm} $1$ \textbf{epoch} $=m$ \textbf{iterations}
%\end{itemize}
\end{minipage}
\hfill%
\begin{minipage}[t]{.33\textwidth}
        \hlo{Solving the RL challenges:}\\[.2cm]
%\begin{enumerate}\compresslist
    $\bullet$~Manage \chall{non-concavity} with \textbf{smooth} policies (\eg Gaussian)\\[.15cm]
    $\bullet$~Approximate \chall{infinite dataset} with a large \textbf{batch size} $N$\\[.15cm]
	$\bullet$~Correct \chall{nonstationarity} with \textbf{importance weighting}	
%\end{enumerate}
\end{minipage}
\hfill%
\begin{minipage}[t]{.31\textwidth}
        \vspace*{-.4cm}
        \hspace*{1.8cm} \emph{Algorithm}
        \vspace*{-.2cm}
        \bookboxx{
                \small
                \textbf{For} $s = 1,\ldots$\\
                \hspace*{.2cm} Sample $N$ trajectories using $\theta^s$\\
                \hspace*{.2cm} Compute FG $\wh{\nabla}_N J(\theta^S)$\\
                \hspace*{.2cm} \textbf{For} $t = 1, \ldots, m-1$\\
                \hspace*{.4cm} Sample $B$ trajectories using $\theta^{s+1}_t$\\
                \hspace*{.4cm} Compute SG $\wh{\nabla}_B J(\theta^{s+1}_t)$ and \\
                \hspace*{.6cm} $c_t^{s+1} = \omega(\theta^{s+1}_t, \theta^s)\wh{\nabla}_B J(\theta^{s+1}_t)$\\
                \hspace*{.4cm} Compute $\theta^{s+1}_{t+1}$ using $\gradBlack{\theta^{s+1}_t}$
        }
\end{minipage}

\begin{center}
        Introducing the \enhance{SVRPG} estimator $\gradBlack{\vtheta}$:
\end{center}

\noindent\dotfill
\begin{tabu} to \textwidth{X[c]X[2c]X[c]}
	\multirow{2}{*}{
		\shortstack{
                \tikz[baseline]{\node[anchor=base,fill=greenp, inner sep=2pt](FGtext){$\textbf{FG term}$};}\\
			$\frac{1}{N}\sum_{i=1}^{N} g(\tau_i|\wt{\vtheta})$\\
			$\tau_i\sim\wt{\vtheta}$\\
			$N$ trajectories\\
			Accurate but \bad{expensive}\\
			$\downarrow$\\
			Updated once per \textbf{epoch}
		}
	}	 
	&\tikz[overlay]{ 
    \node[inner sep=5pt, xshift=-.2cm]{\large{$\gradBlack{\vtheta} := \tikz[baseline]{\node[anchor=base, fill=greenp](FG){$\wh{\nabla}_N J(\wt{\vtheta})$};} + 
            \tikz[baseline]{\node[anchor=base, fill=redp](SG){$\wh{\nabla}_B J({\vtheta})$};} - 
    \tikz[baseline]{\node[anchor=base, fill=yellow](C){$\omega(\vtheta, \wt{\vtheta}) \wh{\nabla}_B J({\wt{\vtheta}})$};}$}
		};
	}  
	\vspace{0.9cm} 
	& \multirow{2}{*}{
		\shortstack{
            \tikz[baseline]{\node[anchor=base, fill=yellow, inner sep=2pt](Ctext){$\textbf{Correction term}$};}\\
			$\frac{1}{B}\sum_{i=1}^{B}\underbrace{\omega(\tau_i|\vtheta,\wt{\vtheta})}_{\textbf{imp. weight}}g(\tau_i|\wt{\vtheta})$\\
			Trajectories from SG term \\
			Ensures SVRG properties\\
			\bad{Distribution mismatch}\\
			$\downarrow$\\
			\textbf{importance weighting}\\
			$\downarrow$\\
			\bad{new source of variance}
		}
	} \\
	& \shortstack{
    \tikz[baseline]{\node[anchor=base, fill=redp, inner sep=2pt](SGtext){$\textbf{SG term}$};}\\
		$\frac{1}{B}\sum_{i=1}^{B} g(\tau_i|\vtheta)$\\
		$\tau_i\sim\vtheta$\\
		$B<<N$ trajectories\\
		Computed at each iteration\\
		\\Cheap but \bad{high-variance}\\
		$\downarrow$\\
		Stabilized by other terms
	}
\end{tabu}
\tikz[overlay]{
        \path[->, greenp, thick] (FG.north west) edge[bend right] (FGtext.east);
        \path[->, yellow, thick] (C.east) edge[bend left] (Ctext.west);
        \draw[->, redp, thick] (SG.south) -- (SGtext.north);
}

@@

\begin{minipage}[t]{.55\textwidth}
	Fundamental \textbf{SVRG} properties:
	\begin{enumerate}
            \item \textcolor{myblue}{\textbf{Unbiasedness:}} $\EVV[]{\gradBlack{\vtheta}} = \gradJ{\vtheta}$
            \item \textcolor{myblue}{\textbf{Vanishing variance:}} $\Var{\gradBlack{\vtheta}}\to0$ as $\vtheta\to\vtheta^*$
	\end{enumerate}
\vfill
\end{minipage}
\hfill%
\begin{minipage}[t]{.4\textwidth}
        \hly{\textbf{Importance weighting}}
